### 2014-11-10 Paper1/paper1.tex
Figs 1 and 2 with some updates to the .tex for paper1.

\pagebreak
\section*{Figures and Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig1.png}
\end{center}
\caption{
{\bf Simulated data illustrating tautology of extraction absent parameter error across pulse and filtered Gaussian noise disturbance types.} Intent is modeled as a minimum jerk, 5th order polynomial. Forces experienced are combined with intent via Burdet et al.'s \cite{burdet2006stability} model to produce the simulated arm trajectory. Extraction to recover intention from arm and force trajectory follows.
}
\label{fig:synthetic}
\end{figure}

>>>>

\pagebreak
\section*{Figures and Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig1.png}
\end{center}
\caption{
{\bf Simulated data illustrating tautology of extraction across pulse and filtered Gaussian noise disturbance types.} Intent is modeled as a minimum jerk, 5th order polynomial. Forces experienced are combined with intent via Burdet et al.'s \cite{burdet2006stability} model to produce the simulated arm trajectory. Extraction to recover intention from arm and force trajectory follows. Parameter errors are introduced into the extraction and varied according to Table 1 to estimate sensitivity. Examining the distribution of trajectories from this analysis reveals that this sensitivity is not uniformly distributed throughout a reach.
}
\label{fig:synthetic}
\end{figure}
